Automated Topic Naming

### 2012-04-02 ese/ese.tex
fix 1 little figure bug
- [X]  Discussion of multiple labels        I did not find the discussion arguing that multiple labels in        Pg were caused by too many terms in each 30-day window to be        convincing. It seems that the overall increase in change-log        words is less than double of that in MySQL (165K words in Pg vs        101K in MySQL), yet the differences in topic overlap appear to        be quite notable. The argument also appears to conflict with an        earlier statement that N=20 was chosen because the overlap in        topics (two topics sharing most frequent terms

A topic analysis tool such as LDA will try to find $N$ independent
word distributions within the word distributions of all input
messages. 
If there are not $N$ independent word distributions, the topics
produced tend to be duplicates of each other, that is, they share the
top terms. During this study we found that if we used a value of 20 for $N$, duplicate topics were infrequent.
Linear combinations of these $N$ word distributions are meant to represent and recreate the word distributions of any of the original messages. In other words, these topics are cross-cutting collections of words relevant to one or more of our commit messages. 
LDA extracts topics in an unsupervised manner; the algorithm relies
solely on the source data and word distributions of messages, with no human intervention.
%We applied Blei's LDA implementation~\cite{Blei2003} against the word distributions of these commits, and generated lists of topics per period.

@@

Figure \ref{fig:best-learn-per-tag} shows that MaxDB and MySQL have
quite different results, as the ROC values for \emph{reliability} and
\emph{functionality} swap between projects. For PostgreSQL, the
performance is nearly always poorer than the other two systems. The
reason for this lack of performance could be that parameter we chose for number of
topics, $N$, could be non-optimal for PostgreSQL. One explanation is that given the size of the PostgreSQL datasets, it was becoming hard to distinguish one topic
from the next. PostgreSQL's data-set was the largest of the 3 projects:
the XML datable that described the PostgreSQL topics that we
annotated was 8 times larger than MySQL and 1.7 times larger than MaxDB. These
size differences arise from the number of commits, the number of files
and the verbosity of the commit descriptions.

%\DONE{expand on why?}

@@

\subfloat[PostgreSQL 7.2]{					
\includegraphics[width=\textwidth]{figures/pgsqln-timeline}
\label{fig:pgsql-timeline}
}
	\caption[]{NFR label per period. Each cell represents a 30-day period. %Numbers represent number of topics in that period labelled with that NFR. 
	Grid cell intensity (saturation) is mapped to label frequency
	relative to the largest label count of \emph{all} NFRs. Grey
	histogram bars indicate label frequency relative to that
	particular NFR's largest label count. Dashed vertical lines
	relate a project milestone (\emph{*Key events*}) to our topic windows.

>>>>

A topic analysis tool such as LDA will try to find $N$ independent
word distributions within the word distributions of all input
messages. 
If there are not $N$ independent word distributions, the topics
produced tend to be duplicates of each other, that is, they share the
top terms. During this study we found that if we used a value of 20
for $N$, duplicate topics were infrequent in MaxDB and MySQL. The
PostgreSQL study was added later and we followed the same methodology
to extract topics fro PostgreSQL, the choice of $N$ = 20 was not
necessarily the optimal choice for PostgreSQL.
Linear combinations of these $N$ word distributions are meant to represent and recreate the word distributions of any of the original messages. In other words, these topics are cross-cutting collections of words relevant to one or more of our commit messages. 
LDA extracts topics in an unsupervised manner; the algorithm relies
solely on the source data and word distributions of messages, with no human intervention.
%We applied Blei's LDA implementation~\cite{Blei2003} against the word distributions of these commits, and generated lists of topics per period.

@@

Figure \ref{fig:best-learn-per-tag} shows that MaxDB and MySQL have
quite different results, as the ROC values for \emph{reliability} and
\emph{functionality} swap between projects. For PostgreSQL, the
performance is nearly always poorer than the other two systems. The
reason for this lack of performance could be that parameter we chose for number of
topics, $N$, could be non-optimal for PostgreSQL. One explanation is that given the size of the PostgreSQL datasets, it was becoming hard to distinguish one topic
from the next. PostgreSQL's data-set was the largest of the 3 projects:
the XML datable that described the PostgreSQL topics that we
annotated was 8 times larger than MySQL and 1.7 times larger than MaxDB. These
size differences arise from the number of commits, the number of files
and the verbosity of the commit descriptions. The density of
information with in the PostgreSQL is a concern as well. Not only are
PostgreSQL commits larger, when raw commit text are compressed with \texttt{gzip} per
each project, PostgreSQL (402kb) is 5.1 times the size of MaxDB (80kb) and 11.8 the size
of MySQL (34kb). PostgreSQL commit messages often include email messages from
the from the mailing list where the patch originated.

% 
\begin{comment}
for file in ~/projects/query1-data/postgresql/query1.mrs2 \
            ~/projects/query1-data/maxdb-7500/dist/query1.mrs2 \
            ~/projects/query1-data/mysql-3.23/query1.mrs2 
do
sort -u $file | egrep "\|200[234]\-[0-9]" | awk -F\| '{print $5}' | sed -e 's/NEWLINE/\n/g' | gzip -c - | wc -c
done
\end{comment}
%\DONE{expand on why?}

@@

\subfloat[PostgreSQL 7.3]{					
\includegraphics[width=\textwidth]{figures/pgsql-timeline}
%\includegraphics[width=\textwidth]{figures/pgsqln-timeline}
\label{fig:pgsql-timeline}
}
	\caption[]{NFR label per period. Each cell represents a 30-day period. %Numbers represent number of topics in that period labelled with that NFR. 
	Grid cell intensity (saturation) is mapped to label frequency
	relative to the largest label count of \emph{all} NFRs. Grey
	histogram bars indicate label frequency relative to that
	particular NFR's largest label count. Dashed vertical lines
	relate a project milestone (\emph{*Key events*}) to our topic windows.
